|

### 2021-11-25 04-Chp-Systematic-Review-Results.Rmd
End of day: 39966
End of day:

---
bibliography: bibliography/references.bib
csl: bibliography/nature.csl
output:
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::word_document2: 
      toc: false
      toc_depth: 3
      reference_docx: templates/word-styles-reference-01.docx
      number_sections: false 
  bookdown::html_document2: default
documentclass: book
---
```{block type='savequote', include=knitr::is_latex_output(),quote_author='(ref:sys-rev-quote)', echo = FALSE}
"It is surely a great criticism of our profession that we have not organised a critical summary by speciality or sub-speciality, up-dated periodically, of all relevant RCTS."  
```

@@

# Systematic review of all available evidence on the association between blood lipids and dementia outcomes {#sys-rev-heading}

@@

<!-- ## To Do -->

<!-- TODO Extra studies to include: -->
<!-- * Larsson - 10.1136/bmj.j5375 [@larsson2017b] -->

@@

@@

Common reasons for exclusion at the full text-stage included studies that reported on the wrong exposures (n = `r n_wrong_exposure` ; most commonly a ineligible lipid fraction), used the wrong study design (n= `r n_study_design`), or reported on a wrong outcome (n=24; e.g. change in cognitive scores).

@@

The two randomised controlled trials provided very weak evidence (`r rct_statin_acd`) of an effect on statin use on all-cause dementia risk (Figure \@ref(fig:rctStatinDementiaFig)).

@@

[_Note: Julian, is this sufficient or should I report statistics for each? Additionally, are there any other sensitivity analyses I should be presenting here?_]

@@

<!-- TODO Check inclusion of Rockwood 2002:  -->
This review has presented a summary of the available evidence on the association between lipids, and treatments that modify lipids such as statins, and the subsequent risk of dementia. This discussion seeks to  to summarise the key findings in terms of literature sources and results as reported. A detailed comparison across the evidence sources, exposure measures and sources of bias reported here is presented as part of the triangulation exercise in Chapter \@ref(tri-heading).

@@

There was some evidence of protective effect of statins on all-cause and Alzheimer's disease dementia when looking at solely at observational studies. This finding was not supported by evidence from the two available RCTs, or by studies that emulated statin treatment using a genetic proxy, suggesting that these findings may be a result of heterogeneity in exposure (e.g. mid-life in studies of lipids with late-life lipid reduction in RCTs) or alternatively due to biases within the non-randomised studies.

@@

Of note, this review did not include the commonly cited PROSPER RCT, which examined the effect of pravastatin on CVD risk, reporting on cognitive outcomes as one of several secondary outcomes.[@shepherd2002a] While widely cited in relation to the effect of statins on dementia risk and included in the Cochrane review of RCTs on this topic,[@mcguinness2016] the trial reported solely on the change in a range of cognitive measures (MMSE, Stroop test, Picture-Word Learning test and others) over follow-up. Though an useful indicator of general cognitive decline, it is not equivalent to a dementia diagnosis using recognised criteria as cognitive tests should feed into a broader diagnostic pathway (see Section \@ref(diagnostic-criteria)). As such, this trial did not met the inclusion criteria for this review.

@@

While conducting this review, I identified several previous systematic reviews of this topic.[@chu2018; @yang2020; @muangpaisan2010; @poly2020;@kuzma2018a; @kuzma2018a] However, this review is the first to use established domain based assessments tools (for example, the RoB 2 tool for randomized controlled trials)[@sterne2019] to assess the risk of bias in included studies. The majority of the highly cited reviews on this topic either do not formally consider risk of bias in the observational studies they include[@chu2018;@power2015] or used a non-domain-based assessment tool (e.g. the Newcastle-Ottowa Scale).[@poly2020]

I identified one previous review of Mendelian randomisation studies examining risk factors for Alzhiemer's disease. However, this review was conducted prior to the majority of Mendelian randomisation studies included in this review being published and extracted results including SNPs in the APoE4 genetic region (see the following section for a discussion of the bias this introduces).

Despite these differences in time-scales and methodology, the duplication of work across reviews (including this review) is substantial. In retrospect, an alternative approach to conducting a further systematic review from scratch could have been employed. Known as an umbrella review, or review-of-reviews, these studies use other systematic reviews rather than primary studies as the unit of analysis.[@aromataris2015; @smith2011] This approach would have enabled more efficient identification of relevant primary studies to which the methods which sets this review apart from other published reviews could have been applied.

@@

### Inclusion of Mendelian randomisations studies {#rev-discussion-MR}

@@

Mendelian randomisation is a powerful analytical technique, using natural variation in participants genomes to identify causal links between a genetically determined risk factor and an outcome, given that the core assumptions detailed in Figure \@ref(fig:mrAssumptions) are valid. However, inclusion of Mendelian randomisation as an acceptable study design in this review was complicated by a number of factors.

@@

Firstly, this study design is relatively new, particularly when compared to randomised trials or cohort studies. Figure \@ref(fig:typeByYear) demonstrates that Mendelian randomisation studies only begin to appear in the evidence base much later than NRSE/NRSI, likely due to the limited availabilt of large scale GWAS datasets needed for two-sample Mendelian randomisation analyses. As such, the process and tools for systematically assessing this study design are not as well developed. A key example of this is in the absence of validated search filters for Mendelian randomisations studies. This limitation is further complicated by the varying terminology used to describe the method, particularly in the early years of it's application, which lead o me including general terms for instrumental variable analyses in my search.

Additionally, there is currently no widely used risk-of-bias assessment tool for Mendelian randomisation studies. A recent commentary provided a checklist  interpreting Mendelian randomisation studies, this guide includes reporting items in their quality checklist. While reporting quality is important, it is a separate consideration to internal validity, as discussed in Section \@ref(risk-of-bias). Similarly, a previous review of Mendelian randomisation studies used the Q-Genie tool which was validated to assess the quality of genetic association studies in meta-analysis.[@sohani2015] While this tool assesses the underlying GWAS used, it does not assess the additional methodological considerations of the Mendelian randomisation analysis itself. <!-- TODO Read this tool. --> For this review, I utilised the best available author-devised tool, sourced from a recent review of systematic reviews of Mendelian randomisation studies.

As a further stumbling block, Mendelian randomisation, particularly when using a two-sample summary data design, is a form of analysis that lends itself to multiple exposure-outcome comparisons. This is particularly relevant to the consideration of bias due to missing evidence. As an example, through snowballing and other measures, I identified at least one relevant Mendelian randomisation study that had not been identified by the search strategy.[@larsson2017b] On review of this paper, the search would not have been expected to find it given the absence of any lipid-related keywords in the title and abstract. The study examined the association between lipid fractions with Alzheimer's disease as one of many risk factors for the condition. Studies such as this can introduce bias into a systematic review, as it is commonly only those risk factors that show a statistically significant result that are reported in the abstract and so are captured by the search. This may bias systematic reviews, including this one, as the analysis of multiple risk factors against a single outcome within a single publication becomes more common. These studies are described as "unknown unknown's" in the context of the RoB-ME tool, and are particularly challenging (as opposed to an analysis that was insufficiently reported to be included in the statistical analysis, or the "known unknown's").

@@

Three relevant preprints from the bioRxiv hits were identified. The added evidential value of including these preprints was described in Section \@ref(sys-rev-including-preprints-res), and indicated that results available only via preprinted reports can contribute substantially to a meta-analysis. Of note, all three included preprints described Mendelian randomisation studies, potentially indicating that more biologically-focused study designs are over-represented in the bioRxiv repository.

@@

I believe there are several aspects where this review is distinct from those reviews already available in the published literature. While several reviews of this research topic exist,[@chu2018; @yang2020; @muangpaisan2010; @poly2020] the overlap between the list of studies included in each is not 100%. As part of this review, I have not only performed a original search of primary literature databases, but have also screened the reference lists of comparable reviews to ensure no study has been omitted. <!-- TODO Though this could --> In addition, this review employed a structured approach to risk-of-bias assessment using a domain-based tool.  This repres important strength of this review, as the detailed risk of bias assessments are used in

@@

In addition, the fact that only a sample of records were dual screened at the title/abstract and full-text stages is a potential limitation, as there is a chance that some eligible records could have been excluded. However,  evidence from assessments of inter- and intra-rater reliability indicate that is is not a major concern.

One particular limitiation with regards to the risk-of-bias assessment is the fact that the ROBINS-E assessments were performed without the tool being finalised. This meant that there were no signalling questions to guide the domain-level risk-of-bias assessment, which may have influenced the accuracy with which domain-level judgements were assigned. However, there is no published empirical evidence supporting the need for signalling questions, and assessment of inter-rater reliability across the different tools did not indicate a specific problem with the ROBINS-E assessments. In fact, low agreement was common across the tools, though this is expected based on the available literature.[@jeyaraman2020]

One further limitation is the fact that the risk of bias due to missing evidence assessment, combined with some empirical evidence that some studies were missed by the search but contained relevant studies is a definite limitation of this review (see Section \@Ref(rev-discussion-MR) above for a fuller discussion of this issue with respect to Mendelian randomisations studies). Unfortunately, this is probably a common limitation across all reviews, based on the way in which increased sensitivity must be balanced with a reasonable workload.

@@

## Conclusions

@@

This work built on the tool introduced in the preceeding chapter (Chapter \ref(sys-rev-tools-heading)), and findings from this review are used though out the subsequent chapters: in Chapter \@ref(cprd-analysis-heading),  summary of the evidence guided the choice of analysis approach, ensuring that the new analysis was at risk of a different source of bias; while in Chapter \@ref(ipd-heading), prospective cohorts identified by the review were contacted in an attempt to obtain individual participant data; finally, the cumulative effect measures calculated here are used as a key source of evidence for the triangulation exercise presented in Chapter \ref(discussion-heading).

>>>>

---
bibliography: bibliography/references.bib
csl: bibliography/nature.csl
output:
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::word_document2: 
      toc: false
      toc_depth: 3
      reference_docx: templates/word-styles-reference-01.docx
      number_sections: false 
  bookdown::html_document2: default
documentclass: book
---
```{block type='savequote', include=knitr::is_latex_output(),quote_author='(ref:sys-rev-quote)', echo = FALSE}
It is surely a great criticism of our profession that we have not organised a critical summary by speciality or sub-speciality, up-dated periodically, of all relevant RCTS.  
```

@@

# Systematic review of existing evidence on the association between blood lipids and dementia outcomes: Results {#sys-rev-results-heading}

@@

@@

## Lay summary

Using the methods outlined in the previous chapter, this chapter presents a systematic review of primary studies that have examined the relationship between the levels of blood lipids (such as cholesterol and triglycerides) and dementia outcomes. In addition, it examined the relationship betweeen treatments that change blood lipid levels, such as statins, and dementia outcomes

My review included `r n_included` primary studies that contained information on this relationship. I found that statins appear to reduce the risk of Alzheimer's disease, but had no effect of vascular dementia. Lipid levels were not associated with any outcome. The methods used in some of the primary studies meant that I was less confident in their results.

The added value of including preprinted study reports, made possible using the tool described in the previous chapter, along with the use of the results of this review in subsequent chapters, is discussed.

## Introduction

@@

Common reasons for exclusion at the full text-stage included studies that reported on ineligible exposures (n = `r n_wrong_exposure` ; most commonly an ineligible lipid fraction) or outcomes (n=24; e.g. change in cognitive scores) or used an ineligible study design (n= `r n_study_design`).

@@

The two randomised controlled trials provided weak evidence (`r rct_statin_acd`) of an effect on statin use on all-cause dementia risk (Figure \@ref(fig:rctStatinDementiaFig)).

@@

<!-- TODO [_Note: Julian, is this sufficient or should I report statistics for each? Additionally, are there any other sensitivity analyses I should be presenting here?_] -->

@@

<!-- TODO Check inclusion of Rockwood 2002:  -->
This review has presented a summary of the available evidence on the association between lipids, and treatments that modify lipids such as statins, and the subsequent risk of dementia. This discussion seeks to summarise the key findings in terms of literature sources and results as reported. A detailed comparison across the evidence sources, exposure measures and sources of bias reported here is presented as part of the triangulation exercise in Chapter \@ref(tri-heading).

@@

There was some evidence of protective effect of statins on all-cause and Alzheimer's disease dementia when looking at solely at observational studies. This finding was not supported by evidence from the two available RCTs, or by studies that emulated statin treatment using a genetic proxy, suggesting that these findings may be a result of heterogeneity in exposure (e.g. mid-life lipid lowering in non-randomised studies versus life-course lipid exposure in Mendelian randomisation studies and late-life lipid reduction in RCTs) or alternatively due to biases within the non-randomised studies.

@@

Of note, this review did not include the commonly cited PROSPER RCT, which examined the effect of pravastatin on CVD risk, reporting on cognitive outcomes as one of several secondary outcomes.[@shepherd2002] While widely cited in relation to the effect of statins on dementia risk and included in the Cochrane review of RCTs on this topic,[@mcguinness2016] the trial reported solely on the change in a range of cognitive measures (MMSE, Stroop test, Picture-Word Learning test and others) over follow-up. Though a useful indicator of general cognitive decline, it is not equivalent to a dementia diagnosis using recognised criteria as cognitive tests should feed into a broader diagnostic pathway (see Section \@ref(diagnostic-criteria)). As such, this trial did not meet the inclusion criteria for this review.

@@

While conducting this review, I identified several previous systematic reviews of this topic.[@chu2018; @yang2020; @muangpaisan2010; @poly2020;@kuzma2018stroke; @kuzma2018risk] However, this review is the first to use established domain based assessments tools (for example, the RoB 2 tool for randomized controlled trials)[@sterne2019] to assess the risk of bias in included studies. The majority of the highly cited reviews on this topic either do not formally consider risk of bias in the observational studies they include[@chu2018;@power2015] or used a non-domain-based assessment tool (e.g. the Newcastle-Ottowa Scale).[@poly2020]

I identified one previous review of Mendelian randomisation studies examining risk factors for Alzheimer's disease. However, this review was conducted prior to the majority of Mendelian randomisation studies included in this review being published and extracted results including SNPs in the APoE4 genetic region (see the following section for a discussion of the bias this introduces).

Despite these differences in timescales and methodology, the duplication of work across reviews (including this review) is substantial. In retrospect, an alternative approach to conducting a further systematic review from scratch could have been employed. Known as an umbrella review, or review-of-reviews, these studies use other systematic reviews rather than primary studies as the unit of analysis.[@aromataris2015; @smith2011] This approach would have enabled more efficient identification of relevant primary studies to which the methods which sets this review apart from other published reviews could have been applied.

@@

### Inclusion of Mendelian randomisation studies {#rev-discussion-MR}

@@

Mendelian randomisation is a powerful analytical technique, using natural variation in participants genomes to identify causal links between a genetically determined risk factor and an outcome, given that the three core assumptions detailed in Figure \@ref(fig:mrAssumptions) are valid. These assumptions are namely that: i) the genetic variant associates with the risk factor of interest (relevance assumption); ii) the variant-exposure association has no unmeasured confounders (independence assumption); and the variants affect the outcome only through their effect on the risk factor of interest (exclusion restriction assumption). However, inclusion of Mendelian randomisation as an acceptable study design in this review was complicated by a number of factors.

todo

@@

Firstly, this study design is relatively new, particularly when compared to randomised trials or cohort studies. Figure \@ref(fig:typeByYear) demonstrates that Mendelian randomisation studies only begin to appear in the evidence base much later than NRSE/NRSI, likely due to the limited availability of large scale GWAS datasets needed for two-sample Mendelian randomisation analyses. As such, the process and tools for systematically assessing this study design are not as well developed. A key example of this is in the absence of validated search filters for Mendelian randomisation studies. This limitation is further complicated by the varying terminology used to describe the method, particularly in the early years of it's application, which lead o me including general terms for instrumental variable analyses in my search.

Additionally, there is currently no widely used risk-of-bias assessment tool for Mendelian randomisation studies. A recent commentary provided a checklist  interpreting Mendelian randomisation studies, this guide includes reporting items in their quality checklist. While reporting quality is important, it is a separate consideration to internal validity, as discussed in Section \@ref(risk-of-bias). Similarly, a previous review of Mendelian randomisation studies used the Q-Genie tool which was validated to assess the quality of genetic association studies in meta-analysis.[@sohani2015] While this tool assesses the underlying GWAS used, it does not assess the additional methodological considerations of the Mendelian randomisation analysis itself. For this review, I used the best available author-devised tool, sourced from a recent review of systematic reviews of Mendelian randomisation studies.[@spiga2021]

As a further stumbling block, Mendelian randomisation, particularly when using a two-sample summary data design, is a form of analysis that lends itself to multiple exposure-outcome comparisons. This is particularly relevant to the consideration of bias due to missing evidence. As an example, through snowballing and other measures, I identified at least one relevant Mendelian randomisation study that had not been identified by the search strategy.[@larsson2017] On review of this paper, the search would not have been expected to find it given the absence of any lipid-related keywords in the title and abstract. The study examined the association between lipid fractions with Alzheimer's disease as one of many risk factors for the condition. Studies such as this can introduce bias into a systematic review, as it is commonly only those risk factors that show a statistically significant result that are reported in the abstract and so are captured by the search. This may bias systematic reviews, including this one, as the analysis of multiple risk factors against a single outcome within a single publication becomes more common. These studies are described as "unknown unknown's" in the context of the RoB-ME tool, and are particularly challenging (as opposed to an analysis that was insufficiently reported to be included in the statistical analysis, or the "known unknown's").

@@

Three relevant preprints from the bioRxiv hits were identified. The added evidential value of including these preprints was described in Section \@ref(sys-rev-including-preprints-res) and indicated that results available only via preprinted reports can contribute substantially to a meta-analysis. Of note, all three included preprints described Mendelian randomisation studies, potentially indicating that more biologically focused study designs are over-represented in the bioRxiv repository.

@@

I believe there are several aspects where this review is distinct from those reviews already available in the published literature. While several reviews of this research topic exist,[@chu2018; @yang2020; @muangpaisan2010; @poly2020] the overlap between the list of studies included in each is not 100%. As part of this review, I have not only performed a original search of primary literature databases, but have also screened the reference lists of comparable reviews to ensure no study has been omitted. <!-- TODO Though this could --> In addition, this review employed a structured approach to risk-of-bias assessment using a domain-based tool.  This represents an important strength of this review, as the detailed risk of bias assessments are used in

@@

In addition, the fact that only a sample of records were dual screened at the title/abstract and full-text stages is a potential limitation, as there is a chance that some eligible records could have been excluded. However,  evidence from assessments of inter- and intra-rater reliability indicate that is not a major concern.

One particular limitation with regards to the risk-of-bias assessment is the fact that the ROBINS-E assessments were performed without the tool being finalised. This meant that there were no signaling questions to guide the domain-level risk-of-bias assessment, which may have influenced the accuracy with which domain-level judgements were assigned. However, there is no published empirical evidence supporting the need for signaling questions, and assessment of inter-rater reliability across the different tools did not indicate a specific problem with the ROBINS-E assessments. In fact, low agreement was common across the tools, though this is expected based on the available literature.[@jeyaraman2020]

One further limitation is the fact that the risk of bias due to missing evidence assessment, combined with some empirical evidence that some studies were missed by the search but contained relevant studies is a definite limitation of this review (see Section \@Ref(rev-discussion-MR) above for a fuller discussion of this issue with respect to Mendelian randomisation studies). Unfortunately, this is probably a common limitation across all reviews, based on the way in which increased sensitivity must be balanced with a reasonable workload.

@@

## Summary

<!-- TODO Clean-up! -->

The results of this review are used to guide the primary analysis presented in Chapter \@ref(cprd-analysis-heading) and \@ref(ipd-heading), by identifying outcomes and analytical techniques that are under-represented in the literature. In addition to forming a key evidence source used in the triangulation exercise presented in Chapter \@ref(tri-heading).

<!-- COMMENT What do you mean guide. Design the SAP or the interpretation or both? -->

@@

 and findings from this review are used though out the subsequent chapters: in Chapter \@ref(cprd-analysis-heading), summary of the evidence guided the choice of analysis approach, ensuring that the new analysis was at risk of a different source of bias; while in Chapter \@ref(ipd-heading), prospective cohorts identified by the review were contacted in an attempt to obtain individual participant data; finally, the cumulative effect measures calculated here are used as a key source of evidence for the triangulation exercise presented in Chapter \ref(discussion-heading).

### 2021-11-25 05-Chp-CPRD-Analysis.Rmd
End of day:

#### Confounding by indication

@@

@@

ggplot2::ggsave(filename = file.path("figures","cprd-analysis","indicationBias.png"),
dagitty::dagitty("dag {
  Statin [exposure,pos=\"0.000,0.000\"]
  \"Vascular outcomes\" [outcome,pos=\"2.000,0.000\"]
  \"Uncontrolled variable\" [pos=\"1.000,1.000\"]
  \"Uncontrolled variable\" -> Statin
  \"Uncontrolled variable\" -> \"Vascular outcomes\"
}") %>% ggdag_classic(size = 6) +
  xlim(-0.5,3) +
  geom_text(data = data.frame(x = 0.316392393234329,
                              y = 0.537705383514239,
                              label = "Prompts"),
            mapping = aes(x = x,
                          y = y,
                          label = label),
            angle = 0L,
            lineheight = 1L,
            hjust = 0.5,
            vjust = 0.5,
            colour = "black",
            family = "sans",
            fontface = "bold",
            inherit.aes = FALSE,
            show.legend = FALSE) +
  geom_text(data = data.frame(x = 0.88,
                              y = 0.05,
                              label = "Induced positive"),
            mapping = aes(x = x,
                          y = y,
                          label = label),
            angle = 0L,
            lineheight = 1L,
            hjust = 0.5,
            vjust = 0.5,
            colour = "black",
            family = "sans",
            fontface = "bold",
            inherit.aes = FALSE,
            show.legend = FALSE) +
  geom_text(data = data.frame(x = 0.88,
                              y = -0.04,
                              label = "association"),
            mapping = aes(x = x,
                          y = y,
                          label = label),
            angle = 0L,
            lineheight = 1L,
            hjust = 0.5,
            vjust = 0.5,
            colour = "black",
            family = "sans",
            fontface = "bold",
            inherit.aes = FALSE,
            show.legend = FALSE) +
  geom_text(data = data.frame(x = 1.65891420807966,
                              y = 0.537705383514239,
                              label = "Causes"),
            mapping = aes(x = x,
                          y = y,
                          label = label),
            angle = 0L,
            lineheight = 1L,
            hjust = 0.5,
            vjust = 0.5,
            colour = "black",
            family = "sans",
            fontface = "bold",
            inherit.aes = FALSE,
            show.legend = FALSE) +
  geom_curve(data = data.frame(x = 0.220612676359188,
                               y = -0.000788829298738025,
                               xend = 1.45,
                               yend = -0.00157828084913909),
             mapping = aes(x = x,
                           y = y,
                           xend = xend,
                           yend = yend),
             linetype = "dashed",
             angle = 0L,
             size = 0.6,
             colour = "black",
             curvature = 0,
             arrow = structure(list(angle = 0,
                                    length = structure(0,
                                                       class = "unit",
                                                       valid.unit = 2L,
                                                       unit = "inches"),
                                    ends = 2L,
                                    type = 2L),
                               class = "arrow"),
             inherit.aes = FALSE,
             show.legend = FALSE) +

  theme_dag(),
width = 8,
height = 3)

@@

### Strengths and limitations

>>>>

#### Confounding by indication {#cprd-confounding-by-ind}

@@

```{r dags, include=F}
```

@@

@@

### Strengths and limitations {#cprd-limitations}

### 2021-11-25 07-Chp-Triangulation.Rmd
End of day:

This triangulation exercise draws on the research produced in each of the preceding chapters. More specifically, this chapter builds on the comprehensive systematic review of existing evidence presented in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading). This evidence base is then supplemented by new evidence on the association of statin use with dementia outcomes in the CPRD (Chapter \@ref(cprd-heading)) and the association of lipids with dementia outcomes in previously unanalysed datasets accessed via the DPUK (Chapter \@ref(ipd-heading)).

@@

As discussed in the introduction to this Chapter (Section \@ref(triangulation-overview)), as part of a narrative synthesis of the evidence all information sources were initally grouped by outcome, and the findings from each source were narratively compared and contrasted. Potential reasons for heterogeneity between study designs were examined with specific reference to the risk-of-bias assessments performed.

@@

@@

The indirectness of a result (also termed external bias, relevance, generalisability, or applicability) is defined here as the discrepancy between the research question addressed by the "idealised" study and the causal question of interest.

@@

As an illustrative example, the bias and indirectness inherent to the estimate of the effect of statin use on Alzheimer's disease in the CPRD are considered here. For this result, there were three domains at greater than low risk of bias: Bias due to confounding, Bias due to definition of the outcome, and Bias in the selection of the reported result (Figure \@ref(fig:biasDirectionSingle)). In Domain 1 (bias due to confounding), the study did not adjust for ApoE4 status, which is predicted to mask any true association between statins and Alzheimer's disease (see Section \@ref(hold) for a fuller discussion). As such, the bias is predicted to _favour the comparator_ and so the absolute direction of bias is to the right. In Domain 7 (bias in measurement of the outcome), there was a high risk of differential misclassification on the basis of the exposure. Here, history of statin use may make a diagnosis of vascular dementia more likely than Alzheimer's disease, and so for this outcome, this bias is predicted to _favour the experiment_ (in this case, an intervention). As such, the absolute direction of bias is to the left. In Domain 7 (bias in selection of the reported result), for consistency with the other NRSI, in the absence of a protocol the bias is assumed to be _away from the null_. Given the position of the effect estimate below the null, the absolute direction of bias in this domain is to the left.

@@

>>>>

This triangulation exercise draws on the research produced in each of the preceding chapters. More specifically, this chapter builds on the comprehensive systematic review of existing evidence presented in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading). This evidence base is then supplemented by new evidence on the association of statin use with dementia outcomes in the CPRD (Chapter \@ref(cprd-analysis-heading)) and the association of lipids with dementia outcomes in previously unanalysed datasets accessed via the DPUK (Chapter \@ref(ipd-heading)).

@@

As discussed in the introduction to this Chapter (Section \@ref(triangulation-overview)), as part of a narrative synthesis of the evidence all information sources were initially grouped by outcome, and the findings from each source were narratively compared and contrasted. Potential reasons for heterogeneity between study designs were examined with specific reference to the risk-of-bias assessments performed.

@@

<!-- TODO Need to include some text here on examples of each: e.g. immortal time bias, or  -->

@@

The indirectness of a result (also termed external bias, external validity, relevance, generalisability, or applicability) is defined here as the discrepancy between the research question addressed by the "idealised" study and the causal question of interest.

@@

As an illustrative example, the bias and indirectness inherent to the estimate of the effect of statin use on Alzheimer's disease in the CPRD are considered here. For this result, there were three domains at greater than low risk of bias: Bias due to confounding, Bias due to definition of the outcome, and Bias in the selection of the reported result (Figure \@ref(fig:biasDirectionSingle)). In Domain 1 (bias due to confounding), the study did not adjust for ApoE4 status, which is predicted to mask any true association between statins and Alzheimer's disease (see Section \@ref(cprd-limitations) for a fuller discussion). As such, the bias is predicted to _favour the comparator_ and so the absolute direction of bias is to the right. In Domain 7 (bias in measurement of the outcome), there was a high risk of differential misclassification on the basis of the exposure. Here, history of statin use may make a diagnosis of vascular dementia more likely than Alzheimer's disease, and so for this outcome, this bias is predicted to _favour the experiment_ (in this case, an intervention). As such, the absolute direction of bias is to the left. In Domain 7 (bias in selection of the reported result), for consistency with the other NRSI, in the absence of a protocol the bias is assumed to be _away from the null_. Given the position of the effect estimate below the null, the absolute direction of bias in this domain is to the left.

@@

<!-- TODO Need to add some text here that says that assessment of the different domains  -->

### 2021-11-25 08-Discussion.Rmd
End of day:

---
output:
  bookdown::word_document2: 
      reference_docx: templates/word-styles-reference-01.docx   
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::html_document2: default
documentclass: book
---

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:intro-quote)', echo = FALSE}
Hold
```
(ref:intro-quote) --- Hold

@@

The first a large scale analysis of blood lipids in the CPRD, which found a slight raised risk of dementia in CPRD patients () with higher LDL-c measured at mid-life, driven by the finding for Alzheimer's disease.[@iwagami2021] These findings are n Not inconsistent with the findings presented in this thesis, particularly given the lack of adjustment for confounding by ApoE4.

<!-- TODO The study says that simulated effect of ApoE4 is a 1.09 RR in the absence of a true causal effect. Main results are between 1.03 and 1.17. CI for most extreme results is (lower = 1.08) is not inconsistent with the effect introduced by ApoE4 which is just a single confounder out of many -->

An analysis of 502,226 participants of the UK BioBank found no association between lipids at mid-life and dementia outcomes (women: TC `r estimate(1.04,.99,1.09,"HR")`, HDL `r estimate(0.95,.83,1.1,"HR")`, LDL `r estimate(1.6,1,1.13,"HR")`/men: TC `r estimate(0.98,.93,1.03,"HR")`, HDL `r estimate(1.1,.95,1.29,"HR")`, LDL `r estimate(.97.91,1.04,"HR")`).[@gong2021] Results were boardly similar between the all-cause dementia, Alzheimer's disease and vascular dementia outcomes. This is comparable to my findings.

@@

This thesis has used multiple sources of evidence to examine the relationship between blood lipids levels and cholesterol risk in a systemtatic manner, including diverse sources of evidence, inclu

@@

@@

>>>>

---
output:
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::word_document2: 
      reference_docx: templates/word-styles-reference-01.docx   
  bookdown::html_document2: default
documentclass: book
---

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:intro-quote)', echo = FALSE}
Since many intra-study biases are difficult or impossible to deal with, the meta-analytic results of observational research are often acts of politics, not science.
```

(ref:intro-quote) --- Alvan R. Feinstein, 1995 [@feinstein1995]

@@

The first a large scale analysis of blood lipids in the CPRD, which found a slight raised risk of dementia in CPRD patients () with higher LDL-c measured at mid-life, driven by the finding for Alzheimer's disease.[@iwagami2021] These findings are  consistent with the findings presented in this thesis, particularly given the lack of adjustment for confounding by ApoE4. <!-- TODO The study says that simulated effect of ApoE4 is a 1.09 RR in the absence of a true causal effect. Main results are between 1.03 and 1.17. CI for most extreme results is (lower = 1.08) is not inconsistent with the effect introduced by ApoE4 which is just a single confounder out of many -->

The UKBioBank is a [@sudlow2015]

A recent analysis of 502,226 participants of this found no association between lipids at mid-life and dementia outcomes (women: TC `r estimate(1.04,.99,1.09,"HR")`, HDL `r estimate(0.95,.83,1.1,"HR")`, LDL `r estimate(1.06,1,1.13,"HR")`/men: TC `r estimate(0.98,.93,1.03,"HR")`, HDL `r estimate(1.1,.95,1.29,"HR")`, LDL `r estimate(.97,.91,1.04,"HR")`).[@gong2021] Results were boardly similar between the all-cause dementia, Alzheimer's disease and vascular dementia outcomes. This is comparable to my findings.

@@

This thesis has used multiple sources of evidence to examine the relationship between blood lipids levels and cholesterol risk in a systematic manner, including diverse sources of evidence, inclu

@@

This should focus on doctors being honesty with patients from the outset and describing what they know regarding the uncertainty of the evidence.

While also recognising that the impact of statin or other LRA use on dementia is going to be secondary to their established effect on lipid-lowering. To even be at risk of developing dementia, patients must survive to old-age, something that is substantially less likely given uncontolled hypercholesterolaemia.

@@

This section should

### 2021-11-25 front-and-back-matter/99-appendices.Rmd
End of day:

## Chapter \@ref(sys-rev-heading) {#appendix-sys-rev}
<!----------------------------------------------------------------------------->

@@

>>>>

## Chapter \@ref(sys-rev-methods-heading) {#appendix-sys-rev}
<!----------------------------------------------------------------------------->

<!-- TODO This needs to be split in two!  -->

@@

## Chapter \@ref(sys-rev-results-heading)

### Dose response plots by fraction

<!----------------------------------------------------------------------------->
(ref:drDemeniaTC-cap) Dose-response meta-analysis of total cholesterol on all-cause dementia

(ref:drDemeniaTC-scap) shortcap

```{r drDemeniaTC, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:drDemeniaTC-cap)', out.width='100%', fig.scap='(ref:drDemeniaTC-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/dr_Dementia_TC.png"))
```
<!----------------------------------------------------------------------------->

<!----------------------------------------------------------------------------->
(ref:drAdLDL-cap) Dose-response meta-analysis of low-density lipoprotein cholesterol on Alzheimer's disease

(ref:drAdLDL-scap) shortcap

```{r drAdLDL, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:drAdLDL-cap)', out.width='100%', fig.scap='(ref:drAdLDL-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/dr_AD_LDL.png"))
```
<!----------------------------------------------------------------------------->
